\chapter*{Acknowledgements}
\renewcommand\chaptermark[1]{\markboth{\uppercase{#1}}{}}
\chaptermark{Acknowledgments}
I would like to express my great appreciation for Professor Migliardi. He accepted to supervise my thesis and he demonstrated a significant willingness to
help me every time I needed. I learnt so much from his tips due to his broad experience with software development and security threats. Thanks to our conversations I fell in love with every aspect of my work. I tried to go in deep on every concept he mentioned because of the curiosity he left me every time we talked about cyber security.\\\\
I would like to express my great appreciation for Professor Nanni. He provided useful information and suggestions during the development of the application.\\\\
I would like to express my gratitude to Dr. Guerar. She introduced me to the world of CAPTCHAs and was available to help me every time I needed. I learnt a lot from her work about cyber security.\\\\
I would like to express my great appreciation for the University of Padova and for the courses I followed. The uncertainty about the future and the idea of lacking the cyber security skills required in a professional environment proved to be significant stimuli to improve myself. Even though I did not know anything about programming when I first applied at the university, I managed to learn a lot and get hooked to it thanks to the professionalism and knowledge demonstrated by the professors. Because of this, during the last five years I have changed a lot and now I spend a lot of my free time programming. Thanks to the University for helping me grow up and thanks to the professors for following my thirst for knowledge.\\\\
I would like to express my gratitude to my family, that taught me to never give up.\\\\
Thanks to Cristina, who taught me that no goals can be reached without someone near you who believes in you and makes you happy.\\\\
Thanks to Francesca, because even if we had many commitments we always managed to find five minutes to stay together and support each other in our choices.\\\\
Thanks to Davide for helping me improving my IT skills with new stimulating ideas and for being near me when I needed.\\\\
Thanks to everyone who has stayed near me and to everyone I met during these years. Each one of you left me something and helped me not to worry and to have 
fun outside the study hours.\\\\