\begin{thebibliography}{9}
%Introduction
\myBibItem{text_audio}{Sarika Choudhary, Ritika Saroha, Yatan Dahiya, and Sachin Choudhary}{Understanding CAPTCHA: Text and Audio Based Captcha with its Applications}{International Journal of Advanced Research in Computer Science and Software Engineering, vol. 3(6), pp. 106-115, 2013}

%State of the Art
\myBibItem{types_CAPTCHA}{Darko Brodi\'c, Alessia Amelio, Radmila Jankovi\'c}{Exploring the influence of CAPTCHA types to the users response time by statistical analysis}{Multimedia Tools and Applications, vol. 77, pp. 12293–12329, 2017}

\myBibItem{survey_advanced_CAPTCHA}{Walid Khalifa Abdullah Hasan}{A Survey of Current Research on Captcha}{International Journal of Computer Science Education in Schools (IJCSES), vol. 7, pp. 141–157, 2016}

\myBibItem{usability_CAPTCHA}{Ruti Gafni, Idan Nagar}{CAPTCHA – Security affecting user experience}{Issues in Informing Science and Information Technology, vol. 13, pp. 63-77, 2016}

\myBibItem{usability_audio}{G. Sauer, J. Holman, J. Lazar, H. Hochheiser, and J. Feng}{Accessible privacy and security: A universally usable human-interaction proof tool}{Univers. Access Inf. Soc., vol. 9, no. 3, p. 239–248, Aug. 2010}

\myBibItem{improving_audio}{Jennifer Tam, Jiri Simsa, David Huggins-Daines, Luis von Ahn, Manuel Blum}{Improving Audio CAPTCHAs}{Symposium On Usable Privacy and Security (SOUPS), 2008}

\myBibItem{DeepCRACk}{William Aiken, Hyoungshick Kim}{POSTER: DeepCRACk: Using Deep Learning to Automatically CRack Audio CAPTCHAs}{Proceedings of the 2018 on Asia Conference on Computer and Communications Security (ASIACCS), 2018}

\myBibItem{break_audio}{Jennifer Tam, Jiri Simsa, Sean Hyde, Luis von Ahn}{Breaking audio CAPTCHAs}{Advances in Neural Information Processing Systems, pp. 1625–1632, 2009}

\myBibItem{game_CAPTCHA}{Manar Mohamed, Song Gao, Nitesh Saxena, Chengcui Zhang}{Dynamic cognitive  game  captcha  usability  and  detection  of  streaming-based  farming}{The Workshop on Usable Security (USEC), co-located with NDSS, 2014}

\myBibItem{survey_CAPTCHA}{Ved Prakash Singh, Preet Pal}{Survey of Different Types of CAPTCHA}{International Journal of Computer Science and Information Technologies (IJCSIT), vol. 5(2), 2014}

\myBibItem{FaceDCAPTCHA}{Goswami G, Powell BM, Vatsa M, Singh R, Noore A}{FaceDCAPTCHA: face detection based color image CAPTCHA}{Future Generation Computer Systems, vol. 31(2), pp. 59–69, 2014}

\myBibItem{Viola_Jones}{Wen-yao Lu, Ming Yang}{Face Detection Based on Viola-Jones Algorithm Applying Composite Features}{International Conference on Robots \& Intelligent System (ICRIS), pp. 82-85, 2019}

\myBibItem{MB_CAPTCHA}{Brian M. Powell, Abhishek Kumar, Jatin Thapar, Gaurav Goswami, Mayank Vatsa, Richa Singh, Afzel Noore}{A multibiometrics-based CAPTCHA for improved online security}{IEEE 8th International Conference on Biometrics Theory, Applications and Systems, 2016}

\myBibItem{math_CAPTCHA}{Carlos Javier Hernandez-Castro, Arturo Ribagorda}{Pitfalls in CAPTCHA design and implementation: The Math CAPTCHA, a case study}{Computers \& Security, vol. 29(1), pp. 141-157, 2010}

\myBibRef{sliding_CAPTCHA}{Luke Wroblewski}{https://www.lukew.com/ff/entry.asp?1138}{A Sliding Alternative to CAPTCHA?}{2010}

\myBibItem{OCR}{Silky Azad, Kiran Jain,}{Captcha: Attacks and weaknesses against OCR technology}{Global Journal of Computer Science and Technology, 2013}

\myBibItem{DECAPTCHA}{E. Bursztein, M. Martin, J. Mitchell}{Text-based CAPTCHA strengths and weaknesses}{Proc. 18th ACM Conference on Computer and Communications Security (CCS), pp. 125–138, 2011}

\myBibItem{Motion_CAPTCHA}{M. Shirali-Shahreza and S. Shirali-Shahreza}{Motion CAPTCHA}{2008 Conference on Human System Interactions, Krakow, pp. 1042-1044, 2008}

\myBibItem{video_attack}{Kameswara Rao Kavya Sri, Gnana Sai}{A Novel Video CAPTCHA Technique to Prevent BOT Attacks}{International Conference on Computational Modeling and  Security (CMS 2016), Procedia Computer  Science, vol. 85, pp. 236–240, 2016}

\myBibItem{video_desc}{K. A. Kluever, R. Zanibbi}{Balancing usability and security in a video captcha}{Proceedings of the 5th Symposium on Usable Privacy and Security, 2009}

\myBibItem{voice_CAPTCHA}{Omar Ahmed Hedaia, Ahmed Shawish, Hana Houssein, Hala Zayed}{Bio-CAPTCHA Voice-Based Authentication Technique for Better Security and Usability in Cloud Computing}{International Journal of Service Science Management Engineering and Technology, vol. 11(2), pp. 59-79, 2020}

\myBibItem{rtCAPTCHA}{Erkam Uzun, Simon Chung}{rtCaptcha: A Real-Time Captcha Based Liveness Detection System}{The Network and Distributed System Security Symposium (NDSS), Georgia Institute of Technology, 2018}

\myBibRef{break_text}{Vinay Shet}{https://security.googleblog.com/2014/12/are-you-robot-introducing-no-captcha.html}{Are you a robot? Introducing "No CAPTCHA reCAPTCHA"}{2014}

\bibitem{google}TehnoBlog, \href{https://tehnoblog.org/google-no-captcha-invisible-recaptcha-first-experience-results-review/}{"Google no Captcha + INVISIBLE reCaptcha–First Experience Results Review"}, \emph{2019}.

\myBibItem{break_google}{Suphannee Sivakorn, Jason Polakis, Angelos D. Keromytis}{I'm not a human: Breaking the Google reCAPTCHA}{Black Hat, pp. 1–12, 2016}

\myBibItem{CAPPCHA}{Meriem Guerar, Alessio Merlo, Mauro Migliardi}{Completely automated public physical test to tell computers and humans apart: A usability study on mobile devices}{Future Generation Computer Systems, vol. 82, pp. 617–630, 2018}

\myBibItem{CAPTCHA_attack_process}{Narges Roshanbin, James Miller}{A survey and analysis of current CAPTCHA approaches}{Journal of Web Engineering, vol. 12, issue 1–2, pp. 1–40, 2013}

%Invisible CAPPCHA
\myBibItem{Invisible_CAPPCHA}{Meriem Guerar, Alessio Merlo, Mauro Migliardi, Francesco Palmieri}{Invisible CAPPCHA: A usable mechanism to distinguish between malware and humans on the mobile IoT}{Computers \& Security, vol. 78, pp. 255–266, 2018}

%Side-channel
\myBibItem{side_leaks}{Shuo Chen, Rui Wang, XiaoFeng Wang, Kehuan Zhang}{Side-Channel Leaks in Web Applications: A Reality Today, a Challenge Tomorrow}{2010 IEEE Symposium on Security and Privacy, pp. 191-20, 2010}

\myBibItem{side_authentication}{Kazuo Sakiyama, Takanori Machida, Arisa Matsubara, Yunfeng Kuai, Yu-ichi Hayashi, Takaaki Mizuki, Noriyuki Miura, Makoto Nagata}{Authentication Using Side-Channel Information.}{IACR Cryptol. ePrint Arch., 2015, 834}

\end{thebibliography}